Computer Science House By-Laws

### 2016-04-11 bylaws.tex
Update bylaws.tex

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}

>>>>

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
